### 2016-09-01 latex/paper.tex
Minor edits

\section{INTRODUCTION}
The earliest bicycles were built in the workshops of carriage makers who adapted the wheel technology of the time. These wheels typically had iron tires, wooden rims, and stout wooden spokes which bore the weight of the machine and rider in compression~\cite{Herlihy2004a}. The spokes needed to be wide enough to prevent lateral buckling and to keep the rim planar, which made them very heavy and limited their maximum diameter. Around 1869, the tension-spoke wheel, an idea proposed in 1808 by Sir George Cayley but never realized, found its first application on the rapidly-developing bicycle~\cite{Ackroyd2011a,Clayton1991b}. Tangential-spoking was developed soon thereafter, and the typical bicycle wheel has not changed dramatically in form since then.

The tension-spoke wheel is a prestressed structure and is susceptible to buckling under internal forces. As the spokes are tightened uniformly, the rim shrinks radially under compression. At a critical spoke tension, the rim becomes unstable and buckles into a non-planar shape. The post-buckling tension vs. displacement curve is generally stable and the original shape of the wheel can often be recovered by reducing the tension. Buckling can also be triggered by external forces in an otherwise stable wheel leading to a release of strain energy. This process can lead to plastic yielding of the rim which makes wheel repair significantly more difficult.

>>>>

\section{INTRODUCTION}
The earliest bicycles were built in the workshops of carriage makers who adapted the wheel technology of the time. These wheels typically had iron tires, wooden rims, and stout wooden spokes which bore the weight of the machine and rider in compression~\cite{Herlihy2004}. The spokes needed to be wide enough to prevent lateral buckling and to keep the rim planar, which made them very heavy and limited their maximum diameter. Around 1869, the tension-spoke wheel, an idea proposed in 1808 by Sir George Cayley but never realized, found its first application on the rapidly-developing bicycle~\cite{Ackroyd2011a,Clayton1991b}. Tangential-spoking was developed soon thereafter, and the typical bicycle wheel has not changed dramatically in form since then.

The tension-spoke wheel is a prestressed structure and is susceptible to buckling under internal forces. As the spokes are tightened uniformly, the rim shrinks radially under compression. At a critical spoke tension, the rim becomes unstable and buckles into a non-planar shape. The average spoke tension remains roughly constant after buckling and the original shape of the wheel can often be recovered by loosening the spokes. Buckling can also be triggered by external forces in an otherwise stable wheel leading to a release of strain energy. This process can lead to plastic yielding of the rim which makes wheel repair significantly more difficult.
